\chapter{前言}

%\largerpage[4]
\largerpage[-1]
本书是我的《语法理论》（\emph{Grammatiktheorie}） \citep{MuellerGTBuch2}这本德语书的扩展版与修订版。\dotfootnote{
本译著是对《语法理论⸺从转换语法到基于约束的理论》（\emph{Grammatical Theory: From Transformational Grammar to Constraint-Based Approaches}）2016年版的翻译（其中第10章参考2018年版）。我们修改了第\ref{chapter-minimalism}章中的错误，并处理了其他一些小问题。⸺译者}
书中介绍了在当代理论学界发挥重要作用，或在过去做出重要贡献的如今仍占据主流地位的各种语法理论。我将这些理论的基本观点进行了解释，并将这些理论应用到德语的“核心语法”中。本书的目标语言仍然采用其德语版中所使用的目标语言，因为很多需要分析的现象不能用英语当作目标语言来解释。而且，很多理论都是在英语的基础上发展起来的，因为这些研究者的母语是英语，将这些理论应用到其他语言的研究中会很有启发性。我将说明这些理论是如何处理论元、附加语、主动/被动转换、局部语序重列（所谓的杂列）、动词位置以及长距离的短语前置（日耳曼语族的语言（除了英语）中动词位于第二位的属性）等现象。
%This book is an extended and revised version of my German book \emph{Grammatiktheorie}
%\citep{MuellerGTBuch2}. It introduces various grammatical theories that play a role in current
%theorizing or have made contributions in the past which are still relevant today. I explain some foundational
%assumptions and then apply the respective theories to what can be called the ``core grammar'' of
%German. I have decided to stick to the object language that I used in the German version of this
%book since many of the phenomena that will be dealt with cannot be explained with English as the object
%language. Furthermore, many theories have been developed by researchers with English as their native
%language and it is illuminative to see these theories applied to another language.
%I show how the theories under consideration deal with arguments and adjuncts, active/passive
%alternations, local reorderings (so-called scrambling), verb position, and fronting of phrases over
%larger distances (the verb second property of the Germanic languages without English).

第二部分探讨对理论发展很重要的根本性问题。这包括我们是否具有语言的内在知识的讨论、人类处理语言的心理语言学的证据的讨论、空语类的地位的讨论，以及我们是整体性地还是组合性地构造和获取话语的问题，也就是，我们是使用短语结构还是词汇结构。
%The second part deals with foundational questions that are important for developing theories.
%This includes a discussion of the question of whether we have innate domain specific knowledge of
%language (UG), the discussion of psycholinguistic evidence concerning the processing of language by
%humans, a discussion of the status of empty elements and of the question whether we construct and perceive utterances 
%holistically or rather compositionally, that is, whether we use phrasal or lexical constructions.

考虑到语言学这一科学领域中有大量的术语是混乱不清的，我在导言部分专门介绍了本书后面章节中将会运用到的术语。第二章介绍短语结构语法，该语法在本书介绍的许多理论中都发挥了重要的作用。我在德语专业本科生的导论课中讲解这两章的内容（除了\ref{sec-PSG-Semantik}有关短语结构语法和语义之间的关系）。高级读者可以略过这些导论性质的章节。后续的章节安排也适用于没有前期知识的读者来理解这些理论的基本内容。有关最新的理论发展的内容更有挑战性：这些内容参见后续将要介绍的章节，以及在现今的理论讨论中相关的其他文献，我们不会在本书中重复表示这些文献，或者对其进行总结。这部分内容可供高水平的学生与学者参考。我将这本书作为高年级本科生研讨课的教材，用它来讲解各种理论的句法方面。这些课件可在我的网页上下载。本书的第二部分更有挑战性，它包括对难点问题和当下研究文献的讨论。
%Unfortunately, linguistics is a scientific field 
%with a considerable amount of terminological chaos. I therefore wrote an introductory
%chapter that introduces terminology in the way it is used later on in the book. The second chapter
%introduces phrase structure grammars, which plays a role for many of the theories that are covered
%in this book. I use these two chapters (excluding the Section~\ref{sec-PSG-Semantik} on interleaving
%phrase structure grammars and semantics) in introductory courses of our BA curriculum for German
%studies. Advanced readers may skip these introductory chapters. The following chapters are
%structured in a way that should make it possible to understand the introduction of the theories
%without any prior knowledge. The sections regarding new developments and classification are more
%ambitious: they refer to chapters still to come and also point to other publications that are
%relevant in the current theoretical discussion but cannot be repeated or summarized in this
%book. These parts of the book address advanced students and researchers. I use this book for teaching
%the syntactic aspects of the theories in a seminar for advanced students in our BA. The slides are
%available on my web page. The second part of the book, the general discussion, is more ambitious and contains the discussion
%of advanced topics and current research literature.

本书只介绍相对较近的理论发展。对于历史文献的回顾，可参见，比如说 \citet{Robins97a-u}和\citet{JL2006a-u}。本书并不包括整
合语言学\isce{整合语言学}{Integrational Linguistics} \citep{Lieb83a-u,Eisenberg2004a,Nolda2007a-u}、
优选论\indexot（\citealp{PS93a-u}；\citealp{Grimshaw97a-u}；G.\ \citealp{GMueller2000a-u}）、角色与参照语法\isce{角色与参照语法}{Role and Reference Grammar} \citep{vanValin93a-ed}以及关系语法
\isce{关系语法}{Relational Grammar} \citep{Perlmutter83a-ed,Perlmutter84b-ed}的内容。我将这些内容留到以后的版本中。
%This book only deals with relatively recent developments. For a historical overview, see for instance
% \citew{Robins97a-u,JL2006a-u}. I am aware of the fact that chapters on
%Integrational Linguistics\is{Integrational Linguistics}
%\citep{Lieb83a-u,Eisenberg2004a,Nolda2007a-u}, Optimality Theory\indexot (\citealp{PS93a-u};
%\citealp{Grimshaw97a-u}; G.\ \citealp{GMueller2000a-u}), Role and Reference Grammar\is{Role and
%  Reference Grammar} \citep{vanValin93a-ed} and Relational Grammar\is{Relational Grammar}
%\citep{Perlmutter83a-ed,Perlmutter84b-ed} are missing. I will leave these theories for later editions.

德语书的最初版本只计划写400页，但是最后的成书规模超出了这一计划：德语教材的第一版有529页，第二版有564页。我在英语版中加入了依存语法和英语的最简语法这两章内容，现在本书有\pageref{LastPage}页。我尽最大努力将所选的理论表述清楚，并列出所有重要的文献。尽管参考文献的列表超过了85页，我也有可能没有列出全部的文献。我对此和其他问题表示歉意。
%The original German book was planned to have 400 pages, but it finally was much bigger: the first
%German edition has 525 pages and the second German edition has 564 pages. I
%added a chapter on Dependency Grammar and one on Minimalism to the English version and now the
%book has \pageref{LastPage} pages. I tried to represent the chosen theories appropriately and to cite all important work. Although the list of
%references is over 85 pages long, I was probably not successful.
%I apologize for this and any other shortcomings.

% There is only one book.
%\input{chapters/versions}

\input{chapters/acknowledgments}
\input{chapters/ontheway}
\input{chapters/langsci}

%\section*{Preface to the Chinese version}
\section*{中译本前言}

%\largerpage
\enlargethispage{8pt}
我非常高兴看到这本语法理论教材翻译成中文。我希望它对很多语言学专业的学生有所帮助。我衷心感谢王璐璐为这本书所付出的努力。我不知道她在建议翻译本书的时候是否知道需要做多少工作。我是不知道的。不管怎样，我很欣慰本书已翻译完成，我们也完成了这个项目。我还要感谢黄思思和孙薇薇。黄思思负责翻译第\ref{Kapitel-CxG}章、第\ref{Abschnitt-Generativ-Modelltheoretisch}章至第\ref{Abschnitt-UG-mit-Hierarchie}章。孙薇薇负责翻译第\ref{Kapitel-LFG}章、第\ref{Kapitel-CG}章和第\ref{Kapitel-TAG}章。王璐璐负责翻译其余各章及全书统稿。\dotfootnote{
王璐璐在中国传媒大学人文学院工作；黄思思在华侨大学华文教育研究院工作；孙薇薇在剑桥大学计算机科学技术系工作，本项翻译任务系其在北京大学王选所工作时完成。⸺译者
}
%、第\ref{Abschnitt-Diskussion-Performanz}章、第\ref{chap-acquisition}章、第\ref{sec-generative-capacity}章、第\ref{Kapitel-Binarybranching-locality-recursion}章、第\ref{Abschnitt-Diskussion-leere-Elemente}章、第\ref{chap-scrambling-extraction-passive}章、第\ref{Abschnitt-Phrasal-Lexikalisch}章、第\ref{Abschnitt-UG-mit-Hierarchie}章。
%Seeing this Chinese version of the grammar theory textbook makes me very happy. I hope it will be useful
%for many students of linguistics. I wholeheartedly want to thank Wang Lulu (王璐璐) for all the efforts she
%put into the book. I am not sure that she knew how much work this was when she suggested to
%translate the book. I did not. In any case I am really grateful that this book is translated and
%that we finished this project. I want to also thank XX (孙薇薇) and XX (黄思思) for translating Chapter~ and Chapter~,
%respectively.

我要感谢在早期的公开评审阶段提出宝贵意见的曹晓玉、刘海涛和王佳骏。我还要感谢14位校对者（%
%\makeatletter\@proofreader\makeatother
陈榕、霍安頔（Andreas Hölzl）、林巧莉、刘畅、李姝姝、练斐、牛若晨、史红改、佟和龙 、屠爱萍、万姝君、王小溪、杨丰榕 、曾巧仪），他们对本译本的一章或几个章节提出了校对意见，他们的工作切实地提高了本译本的质量。我从他们每一个人那里得到的评论都比我从商业出版社获得的评论多得多。我并没有阅读所有的评论，因为它们大部分都是中文，而我并不会汉语。但是王璐璐告诉我，这些评论跟我在英语版所得到的评论一样：很多评论是关于内容的，而不是仅限于错别字和排版的问题。没有一家商业出版机构的校对员能够发现这些小的错误和缺陷，因为商业出版机构的雇员并不懂得本书所涵盖的所有理论知识。这里还需要特别感谢的有冯志伟、刘晓、卢达威、梅德明、夏军、詹卫东，以及Jeroen van de Weijer，他们都为本书提出了许多中肯的意见。
%I also want to thank the XX proofreaders (\makeatletter\@proofreader\makeatother) that each worked on one or more chapters and
%really improved this book. We got more comments from every one of them than I ever got for a book
%done with a commercial publisher. I could not read all of the comments since most of them were in
%Mandarin Chinese, which I do not speak. But Wang Lulu told me that the comments were comparable in
%kind to the comments I got for the English version: some comments were on content rather than on typos and layout
%issues. No proofreader employed by a commercial publisher would have spotted these little mistakes and
%shortcomings since commercial publishers do not have staff that knows all the grammatical
%theories that are covered in this book. 

%~\medskip
%~\\
%\noindent
\begin{flushright}
\begin{tabular}{c@{}}
%斯特凡 $\cdot$ 米勒\\
Stefan Müller\\
柏林\\
\mytodayc%2019年5月9日\\
\end{tabular}
\end{flushright}
%Berlin, \today\hfill Stefan Müller

% lulu/wsun/sisi: DONE
%      <!-- Local IspellDict: en_US-w_accents -->
